Home

### 2017-03-30 analysis/index.Rmd
Files commited by wflow_commit.

>>>>

Click on this [Questions on Algorithm](first-analysis.html) to see more details.

### flash on the chipseq data from Kevin

Click on this [three data sets on the 4500 rows chr1 var_col](sd_chr1_asinh.html) to see more details.

[ns](draft.html)

Click on this [load reslut of GTEx data](GTExresult.html) to see more details.
